---
title: "simulation"
author: "Fenglin Xie"
date: "2025-10-30"
output: github_document
---
你想要验证你的方法对不对，run simulation！
define data generating mechanism which is close to the reality -- draw samples over and over again -- do simulation

```{r}
library(tidyverse)

source("source/sim_mean_sd.R")
```

We can "simulate" by running our function

```{r}
sim_mean_sd(n_subj = 400)
```


Can I "verify" the central limit theorem(大概看一下，而不是严谨证明)

first with a `for` loop

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(30)
  
}

output |> 
  bind_rows() |> 
  ggplot(aes(x = mu_hat)) +
  geom_density()
```


Try to repeat with a map statement

```{r}
sim_results_df =
  expand.grid(
    iter = 1:100,
    sample_size = 30
  ) |> 
  mutate(
    results = map(sample_size, sim_mean_sd)
  ) |> 
  unnest(results)
```

我们想研究--不同的sample size会不会影响结果

##`expand.grid`combine all the possible combinations of the two inputs--30的sample size有1000次，同理其他sample size也是1000次

##一开始做simulation的时候建议从相对较小的数字开始，先确保它确实能运行，之后在把simulation的次数加大

```{r}
sim_results_df =
  expand.grid(
    iter = 1:1000,
    sample_size = c(30, 60, 90, 120)
  ) |> 
  mutate(
    results = map(sample_size, sim_mean_sd)
  ) |> 
  unnest(results)
```


Let's look at this

```{r}
sim_results_df |> 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) |> 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin()
```


Let's try to summarize

(iteration的次数越多，the empirical mean of mu_hat越接近true mean, the empirical sd of mu_hat越接近sd/sqrt(n))

```{r}
sim_results_df |> 
  group_by(sample_size) |> 
  summarize(
    emp_mean = mean(mu_hat),
    emp_sd = sd(mu_hat)
  )
```

Simple linear regression

```{r}
##data generating process

sim_df =
  tibble(
    x = rnorm(30, mean = 1, sd = 1),
    y = 2 + 3 * x + rnorm(30, 0, 1)
  )

##draw plot to show it works

sim_df |> 
  ggplot(aes(x = x, y = y)) +
  geom_point()

slr_fit = lm(y ~ x, data = sim_df)

coef(slr_fit)
```

##do simulation--how do you simulate data, how do you need to analyze it, what you are going to send back as the results

turn this into function. 

```{r}
sim_regression = function(n_subj, beta_0 = 2, beta_1 = 3) {
  
  sim_df =
    tibble(
      x = rnorm(n_subj, mean = 1, sd = 1),
      y = beta_0 + beta_1 * x + rnorm(30, 0, 1)
    )

  slr_fit = lm(y ~ x, data = sim_df)

  tibble(
    beta0_hat = coef(slr_fit)[1],
    beta1_hat = coef(slr_fit)[2]
  )

}
```

```{r}
sim_regression(n_subj = 30)
```

不想手动点击生成，直接使用`for`loop一次性生成大量结果

```{r}
output = vector("list", length = 500)

for (i in 1:500) {
  
  output[[i]] = sim_regression(n_subj = 30)
  
}

output |> 
  bind_rows()
```

##我们设定每次的sample size都是30，但现实中每次获得的sample size 可能都不同，定义不同的sample size即可

```{r}
slr_sim_results_df =
  expand_grid(
    sample_size = 30,
    iter = 1:500
  ) |> 
  mutate(
    results = map(sample_size, sim_regression)
  ) |> 
  unnest(results)

slr_sim_results_df |> 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) +
  geom_point()
```

## One more example
生日问题--一个房间里的人，至少有两个同一天生日

what I am sampling from(1:365),how many sample am I taking(5), 数据可以重复出现（replace = TRUE）-- 取样：从1到365中选5个数字，每个数字可以被重复选取
```{r}
##data generating mechanism 
birthdays = sample(1:365, 5, replace = TRUE)
```

独有的生日个数是否小于5
```{r}
##analysis
repeated_bday = length(unique(birthdays)) < 5

##return the results
repeated_bday

```

put this in a function

```{r}
bday_sim = function(n_room) {
  
  birthdays = sample(1:365, n_room, replace = TRUE)
  
  repeated_bday = length(unique(birthdays)) < n_room
  
  repeated_bday
  
}

bday_sim(5)
```

##如果我知道结果是以true/false的形式展现，那我直接使用`map_lgl`,这样就会直接展示结果，而不是奇怪的数据形式

##为啥是bdays放在map中？？不应该是n_room吗？？
```{r}
bday_sim_results =
  expand_grid(
    bdays = 5:50,
    iter = 1:2500
  ) |> 
  mutate(
    result = map_lgl(bdays, bday_sim)
  ) |> 
  group_by(
    bdays
  ) |> 
  summarize(
    prob_repeat = mean(result)
  )
```

plot this

```{r}
bday_sim_results |> 
  ggplot(aes(x = bdays, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

